The \dealii{} Library, Version 9.2

### 2020-05-29 9.2/paper.tex
reword step-69 slightly

\item \texttt{step-69} presents a first-order scheme solving compressible
Euler's equations of gas dynamics using a graph-based scheme. The time-update
at each node requires the evaluation of a right-hand side that depends
(nonlinearly) on information from the previous time-step that spans more than
one cell. Therefore, assembly loops operate directly on the sparsity graph in
order to retrieve information from the entire stencil associated to each
node. From a programming perspective, \texttt{step-69} features a number of
techniques that are of interest for a wider audience: It discusses a hybrid
thread and MPI parallelized scheme with efficient (MPI node) local
numbering of degrees of freedom. It showcases how to perform asynchronous
write-out of results using a background thread with \texttt{std::async},
and discusses a simple but effective checkpointing and restart technique.

>>>>

\item \texttt{step-69} presents a first-order scheme solving compressible
Euler's equations of gas dynamics with a graph-viscosity stabilization
technique. Beside the usual conservation properties of mass, momentum and
total energy, the method also guarantees that the constructed solution
obeys pointwise stability constraints (positivity of density, internal
energy and a local minimum principle on the specific entropy). As such
\text{step-69} is strictly speaking more a collocation-type discretization
than a variational formulation, even though it is implemented with finite
elements.

The time-update at each node requires the evaluation of a right-hand side
that depends (nonlinearly) on information from the previous time-step that
spans more than one cell. Therefore, assembly loops operate directly on the
sparsity graph in order to retrieve information from the entire stencil
associated to each node. From a programming perspective, \texttt{step-69}
features a number of techniques that are of interest for a wider audience:
It discusses a hybrid thread and MPI parallelized scheme with efficient
(MPI node) local numbering of degrees of freedom. It showcases how to
perform asynchronous write-out of results using a background thread with
\texttt{std::async}, and discusses a simple but effective checkpointing and
restart technique.
